%---------------------------------------------------------------------
% Bibliography
%---------------------------------------------------------------------
%\addcontentsline{toc}{section}{References}
\begin{singlespacing}
\begin{thebibliography}{20}

\bibitem{newton}``America's 60 Best Cities to Live'', 24/7 Wall St., Delaware, MA, 2014, from\\ \url{http://247wallst.com/special-report/2014/09/17/americas-50-best-cities-to-live/13/}

\bibitem{cv} Demaagd, K., Oliver, A., Oostendorp, N., Scott, K., 2012, ``Practical Computer Vision with SimpleCV,'' Ingenuitas, Sebastopol, CA.

\bibitem{haar} Viola, P., Jones, M., 2001, ``Rapid Object Detection using a Boosted Cascade of Simple Features,'' IEEE Computer Society Conference.

\bibitem{blob} Giralt, AS., 2001, ``On texture description,'' Computer Vision Center.

\bibitem{verizon} ``What you can do with Canary Home Security,'' Verizon Wireless, from\\ \url{http://www.verizonwireless.com/mobile-living/home-and-family/canary-wireless-home-security-system/}

\bibitem{comcast} ``Xfinity Home Security Systems, Alarm Systems from Comcast,'' Comcast Xfinity, from \url{http://www.xfinity.com/home-security.html}

\bibitem{adt} ``What is ADT Home Automation?,'' ADT Pulse, from \url{http://www.adtpulse.com/content/adtpulse/en/home/what-is-pulse.html}

\bibitem{simplecv} 2012, “Learn,” Sight Machine, from \url{http://www.simplecv.org/learn/index.html}


\bibitem{audiolaw} Mass. Gen. Laws c. 272, \S $\ $ 99.

\bibitem{condolaw} Mass. Gen. Laws c. 183A.

\bibitem{privacylaw} Mass. Gen. Laws c. 214, \S $\ $ 1B.

\bibitem{scrum} Pathak, P. Saxena, ``Hybrid Methodology Involving Scrum and Waterfall Model towards the Software Project Development in Academic Knowledge Centers,'' International Journal of Evaluation and Research in Education, Vol. 1, No. 1, 2012.

\bibitem{meeting} Department of Electrical Engineering and Technology. (2016, Feb 1). ``Lecture Meeting: Daily stand-up for project ELEC4500--2016''. Wentworth Institute of Technology, Boston, MA.
%\bibitem{practicalelec}
%P. Scherz, S. Monk, \emph{Practical Electronics for Inventors}, McGraw-Hill, New York, 2013.

%\bibitem{artofelectronics}
%P. Horowitz, W. Hill, \emph{The Art of Electronics}, Cambridge University Press, New York, 1989.

%\bibitem{principleselec}
%V. Mehta, \emph{Principles of Electronics: For Diploma, AMIE, Degree \& Other Engineering Examinations}, S. Chand, Ram Nagar, 2010.

%\bibitem{elecprinciples}
%A. Malvino, S. Bates, \emph{Electronic Principles}, McGraw-Hill, New York, 2006.

\end{thebibliography}
\end{singlespacing}