%\begin{multicols}{2}

\newglossaryentry{API}
{
    name=API,
    description={Application Programming Interface is set of tools--usually in the form of a library--to build software-based components and to integrate various technologies.}
}

\newglossaryentry{Blob}
{
    name=blob,
    description={Computer vision method that detects consistent regions within other regions.}
}

\newglossaryentry{Dropbox}
{
    name=Dropbox,
    description={Cloud-based file hosting service that syncs similar-named directories across systems with the configured app.}
}

\newglossaryentry{Google Drive}
{
    name=Google Drive,
    description={Cloud-based file storage and sync service from Google used in this project to draft documents.}
}

\newglossaryentry{GitHub}
{
    name=GitHub,
    description={Online hosting service for git-based source code management and revision control.}
}

\newglossaryentry{Haar}
{
    name=Haar,
    description={Object detection method by P. Viola and M. Jones, \emph{Rapid Object Detection using a Boosted Cascade of Simple Features}.}
}

\newglossaryentry{LAMP}
{
    name=LAMP,
    description={Standard web service stack consisting of open source technologies such as Linux, Apache, MySQL, and Python.}
}

\newglossaryentry{livestream}
{
    name=livestream,
    description={Real-time Internet transmission of an event.}
}

\newglossaryentry{MySQL}
{
    name=MySQL,
    description={My Structured Query Language is a relational database management system released on a GPL v.2 license.}
}

\newglossaryentry{detection}
{
    name=detection,
    description={Techniques to locate objects in still images or video sequences.}
}

\newglossaryentry{recognition}
{
    name=recognition,
    description={Techniques to identify or verify objects in still images or video sequences through a stored database of known faces.}
}

\newglossaryentry{tracking}
{
    name=tracking,
    description={Techniques to locate moving objects in video sequences.}
}

\newglossaryentry{OpenCV}
{
    name=OpenCV,
    description={Open Source Computer Vision is a computer vision library with an open-source BSD license developed at Intel.}
}

\newglossaryentry{open source}
{
    name=open source,
    description={Software and hardware that is released to the public with a free license, allowing for universal access, distribution, and collaborative improvements.}
}

\newglossaryentry{Pi}
{
    name=Raspberry Pi,
    description={The Raspberry Pi is a series of sub-\$50 single-board computers designed for educational usage. For the purposes of this document, all references--unless specified otherwise--refers to the Raspberry Pi 2 Model B.}
}

\newglossaryentry{Plotly}
{
    name=Plotly,
    description={Online data visualization tool with scientific graphing libraries for Python.}
}

\newglossaryentry{REST}
{
    name=REST,
    description={Representational State Transfer is an World Wide Web architectural style for client--server communications.}
}

\newglossaryentry{sighting}
{
    name=sighting,
    description={In this case, each sighting is an interval of time where the system has detected an object.}
}
 
\newglossaryentry{ShareLaTeX}
{
    name=ShareLaTeX,
    description={Online \LaTeX \ editor with revision control and real-time collaboration.}
}
 
\newglossaryentry{SimpleCV}
{
    name=SimpleCV,
    description={Simple Computer Vision is a simplified version of OpenCV. Like OpenCV, SimpleCV is open source.}
}

\newglossaryentry{sprint}
{
    name=sprint,
    description={A basic unit of development in Scrum methodology. It is a timeboxed iteration that contains then existing backlog, current scope of work, and estimated commitment from each resource.}
}

\newglossaryentry{stand-up}
{
    name=stand-up,
    description={A timeboxed meeting at the beginning of the team's workday where each resource gives an update on the events since the last stand-up, the plans for the day, and announces any roadblocks.}
}

\newglossaryentry{VNC}
{
    name=VNC,
    description={Virtual Computing Network is a system used to remotely control another computer.}
}

\newglossaryentry{WebIDE}
{
    name=WebIDE,
    description={Adafruit's web-based Integrated Development Environment designed for the Raspberry Pi.}
}

%\end{multicols}